Scalable Graph-Based Neural \\ Reconstruction for Connectomics

### 2018-03-13 papers/eccv2018/2_method.tex
papers: updated the methods and results section

First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching.
This value is small enough that the skeletons extend into the spines but large enough to keep branching does to a reasonable level.
Additional analysis is available in the supplemental material.
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

>>>>

First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

### 2018-03-13 papers/eccv2018/4_results.tex
papers: updated the methods and results section

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
However, there are some adjacent over-segmented labels which are considered. 
Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
We present additional analysis of the skeletonization parameters in the supplemental material.

\begin{table}
	\centering
	\small
	\setlength{\tabcolsep}{0.75em}
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
		Kasthuri &  & & \\
		FlyEM &  &  & \\
		FIB-25 &  & & \\ \hline
	\end{tabular}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., \TODO{XXX}) compared to total number of edges in the graph (e.g., \TODO{XXXXX}) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
	\label{table:skeletonization}
\end{table}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{Two example segment pairs that we incorrectly prune from our graph. The distances between the circled endpoints are greater than our thresholds.}
	\label{fig:skeleton-results}
\end{figure}

@@

\begin{table}[h]
	\centering
	\small
	\setlength{\tabcolsep}{0.3em}
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% & +3.61\% & -0.53\% & +0.60\% \\
		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\%  & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% & +2.68\% & +0.76\% & +0.66\% \\
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}

>>>>

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
However, there are some adjacent over-segmented labels which are not considered. 
Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
We present additional analysis of the skeletonization parameters in the supplemental material.

\begin{table}
	\centering
	\small
	\setlength{\tabcolsep}{0.75em}
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 610 / 23506 & 556 / 4921 & 214 & 160 \\
		FlyEM & 298 / 17614 & 197 / 4366 & 120 & 19 \\
		FIB-25 &  & & & \\ \hline
	\end{tabular}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 610) compared to total number of edges in the graph (e.g., 23506) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
	\label{table:skeletonization}
\end{table}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}

@@

\begin{table}[h]
	\centering
	\small
	\setlength{\tabcolsep}{0.3em}
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri  &  &  & &  &  & \\
		FlyEM &  & & &  &  &  \\
		Fib-25&  & & & & & \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}
